Measuring causal influence with\\ back-to-back regression

### 2019-05-22 paper/meg_exps.tex
meg_exps"

We aimed to estimate

We show these coefficients as a function of time in the stacked plots, in Figure
\ref{fig:megresult}.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg_result.pdf}
  \caption{Average magnetosensor response across words for one subject.}
  \label{fig:megresult}
\end{figure}

>>>>

We show all the feature coefficients as a function of time in the stacked plots,
Figure \ref{fig:megresult}. Our method confirms previous findings in
neuroscience literature. In particular, \cite{kutas2011thirty} find that word
frequency correlates with a brain wave around 400ms. Similarly,
\cite{pegado2014timing} show that letter strings correlate with early brain
responses. Both these phenomena can be observed in Figures
\label{fig:meg_twocurves} and \ref{fig:megresult}, where we show that our
method is able to separate them more clearly than the forward regression
approach.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg_result.pdf}
  \caption{We plot the coefficients corresponding to each of the features,
  describing their importance over time after stimuli onsets. We can observe that visual features start peaking around 150ms, while lexical features peak around 400ms. We show a similar plot for the Ridge regression baseline (forward) in Figure \ref{fig:ridgebaselineresult}.}
  \label{fig:megresult}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/ridgecv_baseline_result.pdf}
  \caption{Ridge regression baseline. All the coefficients appear to be
  linearly correlated, unlike our method in Figure \ref{fig:megresult}.}
  \label{fig:ridgebaselineresult}
\end{figure}
